---
title: "Beer!"
author: "Eddie Eforo"
date: "2023-12-9"
categories: [news]
---


Oh this is actually pretty cool, I am writing code for the website that I made in class about a data frame that's pretty awesome... Beer! still figuring it out but the following statistics crome from the data frame "https://bcdanl.github.io/data/beer_markets.csv" describing difference beer brands and their quantity and populartity amoung different markets.



```{r}
beer_mkts <- read.csv("https://bcdanl.github.io/data/beer_markets.csv")
```

Variable Description
hh`: an identifier of the household;
X_purchase_desc`: details on the purchased item;
quantity`: the number of items purchased;
brand`: Bud Light, Busch Light, Coors Light, Miller Lite, or Natural Light;
dollar_spent`: total dollar value of purchase;
beer_floz`: total volume of beer, in fluid ounces;
price_per_floz`: price per fl.oz. (i.e., beer spent/beer floz);
container`: the type of container;
promo`: Whether the item was promoted (coupon or otherwise);
market`: Scan-track market (or state if rural);
demographic data, including gender, marital status, household income, class of work, race, education, age, the size of household, and whether or not the household has a microwave or a dishwasher.



```{r}
skimr::skim(beer_mkts)
```

The above is basic summery statistics prior to data transformation. 

After using functions to transform the code we can find more informative and helpful statistics that are more helpful.

 

```{r}
library(dplyr)
library(tidyverse)
beer_mkts %>%
  group_by(market) %>%
  summarise(total_floz = sum(beer_floz)) %>%
  arrange(desc(total_floz)) %>%
  slice_head(n = 5)


```
Here are the top five markets for beer in the united states. it makes sence that the biggest markets are fun citys, with the accept ion of Chicago... they drink becasue their pizza is weird and their Bears fans.


```{r}
beer_mkts %>%
  group_by(brand, market) %>%
  summarise(total_floz = sum(beer_floz)) %>%
  arrange(brand, desc(total_floz)) %>%
  slice_head(n = 5) %>% 
  print(n=25)

```


This shows the top five markets for each individual brand of beer, and it shows how all of Iowa drinks Busch light and nothing else.

